Robust calibration of numerical models based on relative regret

### 2021-09-16 robust_calibration_relative_regret/article.tex
folder structures

\documentclass[preprint,review, 1p]{elsarticle}

@@

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}
% \usepackage{jcomp}
% \usepackage{framed,multirow}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{soul}
\usepackage{verbatim}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\usepackage{graphicx}
\usepackage{booktabs}
% À changer
\newcommand{\yobs}{\mathbf{y}^o}
\DeclareMathOperator*{\argmin}{arg\,min \,}
\DeclareMathOperator*{\argmax}{arg\,max \,}
\newcommand{\Var}{\mathbb{V}\textrm{ar}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\Cov}{\textsf{Cov}}
\newcommand{\tra}{\mathrm{tr}}
\newcommand{\kmean}{{\mathbf{k}}_{\Ex}}
\newcommand{\hatkmean}{\hat{\mathbf{k}}_{\Ex}}
\newcommand{\kvar}{{\mathbf{k}}_{\mathbb{V}}}
\newcommand{\hatkvar}{\hat{\mathbf{k}}_{\mathbb{V}}}
\newcommand{\kmpe}{{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\hatkmpe}{\hat{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\kest}{\hat{\mathbf{k}}}
\newcommand{\RRE}{RRE}
\newcommand{\checkap}{{\alpha}_p}
\newcommand{\checka}{{\alpha}}
\newcommand{\checkk}{\mathbf{k}}
\newcommand{\checkkp}{{\mathbf{k}}_p}
\newcommand{\hatkp}{\hat{\mathbf{k}}_p}
\newcommand{\Kspace}{\mathbb{K}}
\newcommand{\Uspace}{\mathbb{U}}
\newcommand{\JBH}{J_{\mathrm{BH}}}
\newcommand{\JBHS}{J_{\mathrm{BHswap}}}
\DeclareMathOperator*{\esssup}{ess\,sup}
\newcommand{\arthur}[1]{{\itshape\color{cyan} ({#1})}}
\newcommand{\elise}[1]{{\itshape\color{red} ({#1})}}
\newcommand{\victor}[1]{{\itshape\color{blue}}}
\newcommand{\remove}[1]{{\color{red} {}}}
\newcommand{\added}[1]{{\color{teal} #1}}
\usepackage{url}
\usepackage{xcolor}
\definecolor{newcolor}{rgb}{.8,.349,.1}
\usepackage{bbm}
\newlength{\minisize}
\setlength{\minisize}{3cm}
\newlength{\singlecolumnsize}
\setlength{\singlecolumnsize}{9cm}
\newlength{\onehalfcolumn}
\setlength{\onehalfcolumn}{14cm}
\newlength{\fullwidth}
\setlength{\fullwidth}{19cm}
\usepackage{etoolbox}

@@

\newcommand*\linenomathpatchAMS[1]{%
  \expandafter\pretocmd\csname #1\endcsname {\linenomathAMS}{}{}%
  \expandafter\pretocmd\csname #1*\endcsname{\linenomathAMS}{}{}%
  \expandafter\apptocmd\csname end#1\endcsname {\endlinenomath}{}{}%
  \expandafter\apptocmd\csname end#1*\endcsname{\endlinenomath}{}{}%
}
\expandafter\ifx\linenomath\linenomathWithnumbers
  \let\linenomathAMS\linenomathWithnumbers
  %% The following line gets rid of an extra line numbers at the bottom:
  \patchcmd\linenomathAMS{\advance\postdisplaypenalty\linenopenalty}{}{}{}
\else
  \let\linenomathAMS\linenomathNonumbers
\fi
\linenomathpatchAMS{gather}
\linenomathpatchAMS{multline}
\linenomathpatchAMS{align}
\linenomathpatchAMS{alignat}
\linenomathpatchAMS{flalign}
\begin{document}
\linenumbers
%% Title, authors and addresses

@@

%
In this context, for a given $\mathbf{k}$, the set $R_{\alpha}(\mathbf{k}) \subseteq \Uspace$ is defined as the set of $\mathbf{u}$, for which $\mathbf{k}$ is acceptable:
\begin{linenomath*}
\begin{equation}
\label{eq:def_Ralpha}
R_{\alpha}(\mathbf{k}) = \left\{ \mathbf{u} \in \Uspace \mid J(\mathbf{k},\mathbf{U}=\mathbf{u}) \leq \alpha J^*(\mathbf{u}) \right\}
\end{equation}
\end{linenomath*}

@@

This linked to the definition of the distribution of the minimisers $\mathbf{K}^*$. For instance, if $\Kspace$ is a discrete set, \added{$\mathbf{K}^*$ is a discrete random variable}, and we can rewrite $\Gamma_1$ as $\Gamma_1(\mathbf{k})=\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U}=\mathbf{u}) = J^*(\mathbf{U})\right] = \Prob_{\mathbf{U}}\left[\mathbf{k} = \mathbf{k}^*(\mathbf{U})\right]$ which is the probability mass function of $\mathbf{K}^*$.

@@

\bibliographystyle{model1-num-names} 
\bibliography{bibexport.bib}

>>>>

\documentclass[preprint, review, 1p]{elsarticle}

@@

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}
%\usepackage{jcomp}
% \usepackage{framed,multirow}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{soul}
\usepackage{verbatim}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\usepackage{graphicx}
\usepackage{booktabs}
% À changer
\newcommand{\yobs}{\mathbf{y}^o}
\DeclareMathOperator*{\argmin}{arg\,min \,}
\DeclareMathOperator*{\argmax}{arg\,max \,}
\newcommand{\Var}{\mathbb{V}\textrm{ar}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\Cov}{\textsf{Cov}}
\newcommand{\tra}{\mathrm{tr}}
\newcommand{\kmean}{{\mathbf{k}}_{\Ex}}
\newcommand{\hatkmean}{\hat{\mathbf{k}}_{\Ex}}
\newcommand{\kvar}{{\mathbf{k}}_{\mathbb{V}}}
\newcommand{\hatkvar}{\hat{\mathbf{k}}_{\mathbb{V}}}
\newcommand{\kmpe}{{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\hatkmpe}{\hat{\mathbf{k}}_{\mathrm{MPE}}}
\newcommand{\kest}{\hat{\mathbf{k}}}
\newcommand{\RRE}{RRE}
\newcommand{\checkap}{{\alpha}_p}
\newcommand{\checka}{{\alpha}}
\newcommand{\checkk}{\mathbf{k}}
\newcommand{\checkkp}{{\mathbf{k}}_p}
\newcommand{\hatkp}{\hat{\mathbf{k}}_p}
\newcommand{\Kspace}{\mathbb{K}}
\newcommand{\Uspace}{\mathbb{U}}
\newcommand{\JBH}{J_{\mathrm{BH}}}
\newcommand{\JBHS}{J_{\mathrm{BHswap}}}
\DeclareMathOperator*{\esssup}{ess\,sup}
\newcommand{\arthur}[1]{{\itshape\color{cyan} ({#1})}}
\newcommand{\elise}[1]{{\itshape\color{red} ({#1})}}
\newcommand{\victor}[1]{{\itshape\color{blue}}}
\newcommand{\remove}[1]{{\color{red} {}}}
\newcommand{\added}[1]{% {\color{teal}
    #1}
\usepackage{url}
\usepackage{xcolor}
\definecolor{newcolor}{rgb}{.8,.349,.1}
\usepackage{bbm}
\newlength{\minisize}
\setlength{\minisize}{3cm}
\newlength{\singlecolumnsize}
\setlength{\singlecolumnsize}{9cm}
\newlength{\onehalfcolumn}
\setlength{\onehalfcolumn}{14cm}
\newlength{\fullwidth}
\setlength{\fullwidth}{19cm}
\usepackage{etoolbox}

@@

\begin{document}
% \linenumbers
%% Title, authors and addresses

@@

%
In this context, for a given $\mathbf{k}$, the set $R_{\alpha}(\mathbf{k}) \subseteq \Uspace$ is defined as the set of $\mathbf{u}$, for which $\mathbf{k}$ is acceptable:
\begin{linenomath*}
\begin{equation}
\label{eq:def_Ralpha}
R_{\alpha}(\mathbf{k}) = \left\{ \mathbf{u} \in \Uspace \mid J(\mathbf{k},\mathbf{u}) \leq \alpha J^*(\mathbf{u}) \right\}
\end{equation}
\end{linenomath*}

@@

This linked to the definition of the distribution of the minimisers $\mathbf{K}^*$. For instance, if $\Kspace$ is a discrete set, \added{$\mathbf{K}^*$ is a discrete random variable}, and we can rewrite $\Gamma_1$ as $\Gamma_1(\mathbf{k})=\Prob_{\mathbf{U}}\left[J(\mathbf{k},\mathbf{U}) = J^*(\mathbf{U})\right] = \Prob_{\mathbf{U}}\left[\mathbf{k} = \mathbf{k}^*(\mathbf{U})\right]$ which is the probability mass function of $\mathbf{K}^*$.

@@

\bibliographystyle{model1-num-names} 
\bibliography{}
